---
title: "Prosody: Experiment 2"
output: 
  html_document:
    toc: true
---


```{r include=FALSE}
library(tidyverse)
library(forcats)
library(lme4)
```

# Reading in data

```{r}
# setwd("/Users/seantrott/Dropbox/UCSD/Research/IndirectSpeechActs/Prosody/prosody_indirect_requests/analysis/exp2/")
coded = read.csv("../../data/exp2/exp2_critical.csv")

```


## Checking over data

```{r}
length(unique(coded$subject))
```

# Can people detect a signal, generally?

## Descriptive

```{r}
mean(coded$correct)
```


## Visualization
```{r}
coded %>%
  ggplot(aes(x = form, y = numeric_response, fill = condition)) +
  geom_bar(stat="summary", position="dodge", fun.y="mean") +
  stat_summary (fun.y = function(x){mean(x)},
                fun.ymin = function(x){mean(x) - 1*sd(x)/sqrt(length(x))},
                fun.ymax = function(x){mean(x) + 1*sd(x)/sqrt(length(x))},
                geom= 'pointrange', 
                position=position_dodge(width=0.95)) +
  theme_minimal() +
  ggtitle("Request interpretations by condition") +
  xlab("Condition") +
  ylab("Percent choosing 'request'") +
  scale_y_continuous(limits = c(0, 1))
```

## Analysis

Both `form` and `condition` explain significant sources of variance in participants' responses.


```{r}

m1_full = glmer(data=coded, response ~ condition + form + 
                       (1 + condition | stimNum) +
             (1 + condition + form | subject),
           control=glmerControl(optimizer="bobyqa"),
         family=binomial())

m1_no_form = glmer(data=coded, response ~ condition + (1 + condition | stimNum) +
             (1 + condition + form | subject),
           control=glmerControl(optimizer="bobyqa"),
         family=binomial())


m1_no_condition = glmer(data=coded, response ~ form + (1 + condition | stimNum) +
             (1 + condition + form | subject),
           control=glmerControl(optimizer="bobyqa"),
         family=binomial())


anova(m1_full, m1_no_form)
anova(m1_full, m1_no_condition)

summary(m1_full)
```


# How does accuracy interact with other factors?

# Already heard utterance

```{r}
m1 = glmer(data=coded, correct ~ already_heard_by_speaker + 
             (1 + already_heard_by_speaker | stimNum) +
             (1 | subject),
           control=glmerControl(optimizer="bobyqa"),
         family=binomial())

m1.reduced =glmer(data=coded, correct ~ (1 + already_heard_by_speaker | stimNum) +
                    (1 | subject),
                  control=glmerControl(optimizer="bobyqa"),
                    family=binomial())

anova(m1, m1.reduced)
```

```{r}
coded %>%
  ggplot(aes(x = form, y = correct, fill = already_heard_by_speaker)) +
  geom_bar(stat="summary", position="dodge", fun.y="mean") +
  stat_summary (fun.y = function(x){mean(x)},
                fun.ymin = function(x){mean(x) - 1*sd(x)/sqrt(length(x))},
                fun.ymax = function(x){mean(x) + 1*sd(x)/sqrt(length(x))},
                geom= 'pointrange', 
                position=position_dodge(width=0.95)) +
  theme_minimal() +
  labs(x = "Already heard utterance",
       y = "Accuracy",
       title = "Accuracy by form and speaker") +
  geom_hline(yintercept=.5, colour="black", linetype="dotted")
```


## Visualization 

```{r}
coded %>%
  ggplot(aes(x = speaker, y = correct, fill = form)) +
  geom_bar(stat="summary", position="dodge", fun.y="mean") +
  stat_summary (fun.y = function(x){mean(x)},
                fun.ymin = function(x){mean(x) - 1*sd(x)/sqrt(length(x))},
                fun.ymax = function(x){mean(x) + 1*sd(x)/sqrt(length(x))},
                geom= 'pointrange', 
                position=position_dodge(width=0.95)) +
  theme_minimal() +
  labs(x = "Speaker",
       y = "Accuracy",
       title = "Accuracy by form and speaker") +
  geom_hline(yintercept=.5, colour="black", linetype="dotted")

```

## Analysis

### Building the models
```{r}

m1 = glmer(data=coded, correct ~ form*speaker + already_heard_by_speaker + (1 | stimNum) +
             (1 + form | subject),
           control=glmerControl(optimizer="bobyqa"),
         family=binomial())

m1.reduced =glmer(data=coded, correct ~ form + speaker + already_heard_by_speaker + (1 | stimNum) +
                    (1 + form | subject),
                  control=glmerControl(optimizer="bobyqa"),
                    family=binomial())

m1.reduced.form = glmer(data=coded, correct ~ form + already_heard_by_speaker + (1 | stimNum) +
                    (1 + form | subject),
                  control=glmerControl(optimizer="bobyqa"),
                    family=binomial())

m1.reduced.speaker = glmer(data=coded, correct ~ speaker + already_heard_by_speaker +(1 | stimNum) +
                    (1 + form | subject),
                  control=glmerControl(optimizer="bobyqa"),
                    family=binomial())

m1.null = glmer(data=coded, correct ~ already_heard_by_speaker +(1 | stimNum) +
                    (1 + form | subject),
                  control=glmerControl(optimizer="bobyqa"),
                    family=binomial())


```

### Model comparisons

All models constructed with random slopes for effect of speaker per item, and random slopes for effect form per subject.


```{r}
anova(m1, m1.reduced)
anova(m1.reduced, m1.reduced.form)
anova(m1.reduced, m1.reduced.speaker)
anova(m1.reduced.form, m1.null)
anova(m1.reduced.speaker, m1.null)
```

## Analysis

```{r}

m1.order =glmer(data=coded, correct ~ Order + (1 | stimNum) +
                    (1 | subject),
                  control=glmerControl(optimizer="bobyqa"),
                  family=binomial())

m1.null =glmer(data=coded, correct ~ (1 | stimNum) +
                    (1 | subject),
                  control=glmerControl(optimizer="bobyqa"),
                  family=binomial())

anova(m1.order,m1.null)
```

## Order by block

It might also be the case that accuracy improves for each block. 


```{r}

coded$order_by_block = coded$Order %% 12
table(coded$order_by_block)

# Recode the 0s from this procedure
coded$order_by_block = ifelse(coded$order_by_block == 0, 12, coded$order_by_block)

m1.order_with_speaker_interaction =glmer(data=coded, correct ~ order_by_block * speaker + (1 | stimNum) +
                    (1 | subject),
                  control=glmerControl(optimizer="bobyqa"),
                  family=binomial())

m1.order_plus_speaker =glmer(data=coded, correct ~ order_by_block + speaker + (1 | stimNum) +
                    (1 | subject),
                  control=glmerControl(optimizer="bobyqa"),
                  family=binomial())


m1.only_speaker =glmer(data=coded, correct ~ speaker + (1 | stimNum) +
                    (1 | subject),
                  control=glmerControl(optimizer="bobyqa"),
                  family=binomial())

m1.order_by_block =glmer(data=coded, correct ~ order_by_block + (1 | stimNum) +
                    (1 | subject),
                  control=glmerControl(optimizer="bobyqa"),
                  family=binomial())

m1.null =glmer(data=coded, correct ~ (1 | stimNum) +
                    (1 | subject),
                  control=glmerControl(optimizer="bobyqa"),
                  family=binomial())

anova(m1.order_with_speaker_interaction, m1.order_plus_speaker)
anova(m1.order_plus_speaker, m1.only_speaker)
anova(m1.order_by_block, m1.null)
```


# Analysis of acoustic features

Now we load the raw audio files and try to predict subject's responses from acoustic features. We follow the z-scaling procedure reported in Trott & Bergen (2019, CogSci submission).

## Dataset

```{r}
df_audio = read_csv("../../data/audio_features/audio_features.csv")
df_audio$label = factor(df_audio$label)

df_audio$label = fct_recode(df_audio$label,
                            "Request" = "IR",
                            "Non-Request" = "Literal")


df_audio$speaker = factor(df_audio$speaker)

df_audio = df_audio %>% 
  group_by(speaker) %>% 
  mutate(mean_f0_z_score = scale(mean_f0),
         duration_f0_z_score = scale(duration_f0),
         range_f0_z_score = scale(range_f0),
         sd_f0_z_score = scale(sd_f0),
         slope_f0_z_score = scale(slope_f0),
         mean_intensity_z_score = scale(mean_intensity),
         sd_intensity_z_score = scale(sd_intensity)
         )
```



## Merge datasets

```{r}
df_audio$item = factor(paste(df_audio$speaker, df_audio$stimNum, df_audio$label, sep="_"))
coded$item = factor(paste(coded$speaker, coded$stimNum, coded$condition, sep = "_"))

new_df = data.frame(item=df_audio$item, 
                    mean_f0_z_score=df_audio$mean_f0_z_score, 
                    duration_f0_z_score=df_audio$duration_f0_z_score,
                    range_f0_z_score=df_audio$range_f0_z_score,
                    sd_f0_z_score=df_audio$sd_f0_z_score,
                    slope_f0_z_score=df_audio$slope_f0_z_score,
                    mean_intensity_z_score=df_audio$mean_intensity_z_score,
                    sd_intensity_z_score=df_audio$sd_intensity_z_score)


merged = merge(coded, new_df, by="item")
nrow(coded)
nrow(merged)


merged$response = fct_recode(merged$response,
                             "Request" = "request",
                             "Non-Request" = "literal")
merged$response = factor(merged$response, levels=c("Request", "Non-Request"))
merged$form = factor(merged$form, levels=c("nonconventional", "conventional"))

```



## Analysis

Now we ask whether adding acoustic features to the model predicts participants' **responses**, above and beyond the variance explained by *form* and *speaker* (and their interaction). 

To do this, we compare each model in turn, successively dropping out different acoustic features.

Random effects include random intercepts for subjects and items. Including a random slope for the effect of form for items (as in the models above) prevents the models from converging. (That said, analysis of these models suggests very similar results.)

### Do the features predict participants' predicted label?

```{r}
model_response_full = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                       duration_f0_z_score * form +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        form * speaker + 
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())


summary(model_response_full)
```

#### F0 slope

```{r}
model_response_no_slope_interaction = glmer(data = merged,
                      response ~ slope_f0_z_score +
                      mean_f0_z_score * form +
                      duration_f0_z_score * form +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_slope = glmer(data = merged,
                      response ~ mean_f0_z_score * form +
                       duration_f0_z_score * form +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_response_full, model_response_no_slope_interaction)
anova(model_response_no_slope_interaction, model_response_no_slope)

```

#### Mean F0

```{r}
model_response_no_mean_f0_interaction = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                        mean_f0_z_score +
                       duration_f0_z_score * form +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_mean_f0 = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                       duration_f0_z_score * form +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_response_full, model_response_no_mean_f0_interaction)
anova(model_response_no_mean_f0_interaction, model_response_no_mean_f0)

```

#### F0 duration (number of voiced frames)

```{r}
model_response_no_f0_dur_interaction = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                       duration_f0_z_score +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_f0_dur = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        already_heard_by_speaker +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_response_full, model_response_no_f0_dur_interaction)
anova(model_response_no_f0_dur_interaction, model_response_no_f0_dur)

```



#### F0 range

```{r}
model_response_no_f0_range_interaction = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                       duration_f0_z_score * form +
                       range_f0_z_score +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_f0_range = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                       duration_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_response_full, model_response_no_f0_range_interaction)
anova(model_response_no_f0_range_interaction, model_response_no_f0_range)

```


#### SD F0

```{r}
model_response_no_f0_sd_interaction = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                       duration_f0_z_score * form +
                       range_f0_z_score * form+
                       sd_f0_z_score +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_f0_sd = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                        range_f0_z_score * form+
                       duration_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_response_full, model_response_no_f0_sd_interaction)
anova(model_response_no_f0_sd_interaction, model_response_no_f0_sd)

```

#### Mean Intensity

```{r}
model_response_no_mean_intensity_interaction = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                       duration_f0_z_score * form +
                       range_f0_z_score * form+
                       sd_f0_z_score * form +
                       mean_intensity_z_score +
                       sd_intensity_z_score * form +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_mean_intensity = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                        range_f0_z_score * form+
                        sd_f0_z_score * form +
                       duration_f0_z_score * form +
                       sd_intensity_z_score * form +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_response_full, model_response_no_mean_intensity_interaction)
anova(model_response_no_mean_intensity_interaction, model_response_no_mean_intensity)

```

#### SD Intensity

```{r}
model_response_no_sd_intensity_interaction = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                       duration_f0_z_score * form +
                       range_f0_z_score * form+
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_sd_intensity = glmer(data = merged,
                      response ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                        range_f0_z_score * form+
                        sd_f0_z_score * form +
                       duration_f0_z_score * form +
                       mean_intensity_z_score * form +
                        form * speaker +
                        already_heard_by_speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_response_full, model_response_no_sd_intensity_interaction)
anova(model_response_no_sd_intensity_interaction, model_response_no_sd_intensity)
```

### Multiple comparisons correction

```{r}
p1 = anova(model_response_full, model_response_no_slope_interaction)$`Pr(>Chisq)`[2]
p2 = anova(model_response_no_slope_interaction, model_response_no_slope)$`Pr(>Chisq)`[2]
p3 = anova(model_response_full, model_response_no_mean_f0_interaction)$`Pr(>Chisq)`[2]
p4 = anova(model_response_no_mean_f0_interaction, model_response_no_mean_f0)$`Pr(>Chisq)`[2]
p5 = anova(model_response_full, model_response_no_f0_dur_interaction)$`Pr(>Chisq)`[2]
p6 = anova(model_response_no_f0_dur_interaction, model_response_no_f0_dur)$`Pr(>Chisq)`[2]
p7 = anova(model_response_full, model_response_no_f0_range_interaction)$`Pr(>Chisq)`[2]
p8 = anova(model_response_no_f0_range_interaction, model_response_no_f0_range)$`Pr(>Chisq)`[2]
p9 = anova(model_response_full, model_response_no_f0_sd_interaction)$`Pr(>Chisq)`[2]
p10 = anova(model_response_no_f0_sd_interaction, model_response_no_f0_sd)$`Pr(>Chisq)`[2]
p11 = anova(model_response_full, model_response_no_mean_intensity_interaction)$`Pr(>Chisq)`[2]
p12 = anova(model_response_no_mean_intensity_interaction, model_response_no_mean_intensity)$`Pr(>Chisq)`[2]
p13 = anova(model_response_full, model_response_no_sd_intensity_interaction)$`Pr(>Chisq)`[2]
p14 = anova(model_response_no_sd_intensity_interaction, model_response_no_sd_intensity)$`Pr(>Chisq)`[2]

p.adjust(c(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, p13, p14), method="holm")

```


# Merging with by-item norms

Finally, we merge the data with the by-item norms, which give us *mean* request ratings for each item. We see that both `form` and `prior request likelihood` predict participants' responses.

```{r}
coded_item_means = read_csv("../../data/exp3/item_means.csv")

merged_with_means = merge(merged, coded_item_means, by = c("stimNum", "form", "topic"))
nrow(merged)
nrow(merged_with_means)
```


```{r}
merged_with_means$form = factor(merged_with_means$form, levels = c("nonconventional", "conventional"))

merged_with_means$response = factor(merged_with_means$response, levels=c("Non-Request", "Request"))
merged_with_means$condition = factor(merged_with_means$condition, levels=c("Non-Request", "Request"))


model_response_full = glmer(data = merged_with_means,
                      response ~ form + condition + mean_request +
                        (1 + condition + form + mean_request | subject),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_prior = glmer(data = merged_with_means,
                      response ~ form + condition +
                        (1 + condition + form + mean_request | subject),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_condition = glmer(data = merged_with_means,
                      response ~ form + mean_request +
                        (1 + condition + form + mean_request | subject),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())


anova(model_response_full, model_response_no_prior)
anova(model_response_full, model_response_no_condition)


summary(model_response_full)

```


