---
title: 'Experiment 1: Acoustic Features'
output: html_document
---


```{r include=FALSE}
library(tidyverse)
library(forcats)
library(lme4)
```


# Introduction

Can we predict accuracy on Experiment 1 with the acoustic features?

# Load data

## Audio features

Now we load the raw audio files and try to predict subject's responses from acoustic features. We follow the z-scaling procedure reported in Trott & Bergen (2019, CogSci submission).

```{r}
# setwd("/Users/seantrott/Dropbox/UCSD/Research/IndirectSpeechActs/Prosody/prosody_indirect_requests/analysis/exp1")
df_audio = read_csv("../../data/audio_features/audio_features.csv")
df_audio$label = factor(df_audio$label)

df_audio$label = fct_recode(df_audio$label,
                            "request" = "IR",
                            "literal" = "Literal")

df_audio = df_audio %>% 
  group_by(speaker) %>% 
  mutate(mean_f0_z_score = scale(mean_f0),
         duration_f0_z_score = scale(duration_f0),
         range_f0_z_score = scale(range_f0),
         sd_f0_z_score = scale(sd_f0),
         slope_f0_z_score = scale(slope_f0),
         mean_intensity_z_score = scale(mean_intensity),
         sd_intensity_z_score = scale(sd_intensity)
         )
```


## Experimental data

```{r}

experimental_data = read.csv("../../data/exp1/experiment1_concat_full.csv")
experimental_data = filter(experimental_data, answer %in% c("first", "second"))



experimental_data$speaker_recoded = fct_recode(experimental_data$speaker,
                           "S1" = "Danny",
                           "S2" = "Karen",
                           "S3" = "Katie",
                           "S4" = "Maiyi",
                           "S5" = "Nimish")

experimental_data$item = factor(paste(experimental_data$speaker_recoded, experimental_data$stimNum, sep = "_"))

experimental_data$form = fct_recode(experimental_data$form,
                           "conventional" = "modal",
                           "nonconventional" = "indirect")


```


# Analysis of acoustic features

## All forms

```{r}
model_all_features_all = glmer(data = df_audio,
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  slope_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())

model_reduced_no_slope = glmer(data = df_audio,
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())


model_reduced_no_mean_f0 = glmer(data = df_audio,
                label ~ slope_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())


model_reduced_no_range = glmer(data = df_audio,
                label ~ mean_f0_z_score + 
                  slope_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())


model_reduced_no_sd_f0 = glmer(data = df_audio,
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  slope_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())

model_reduced_no_duration = glmer(data = df_audio,
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  slope_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())

model_reduced_no_mean_intensity = glmer(data = df_audio,
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  slope_f0_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())

model_reduced_no_sd_intensity = glmer(data = df_audio,
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  slope_f0_z_score +
                  (1 | topic),
                 family = binomial())
```

### Correct

```{r}
summary(model_all_features_all)

anova(model_all_features_all, model_reduced_no_slope)
anova(model_all_features_all, model_reduced_no_mean_f0)
anova(model_all_features_all, model_reduced_no_range)
anova(model_all_features_all, model_reduced_no_sd_f0)
anova(model_all_features_all, model_reduced_no_duration)
anova(model_all_features_all, model_reduced_no_mean_intensity)
anova(model_all_features_all, model_reduced_no_sd_intensity)

p1 = anova(model_all_features_all, model_reduced_no_slope)$`Pr(>Chisq)`[2]
p2 = anova(model_all_features_all, model_reduced_no_mean_f0)$`Pr(>Chisq)`[2]
p3 = anova(model_all_features_all, model_reduced_no_range)$`Pr(>Chisq)`[2]
p4 = anova(model_all_features_all, model_reduced_no_sd_f0)$`Pr(>Chisq)`[2]
p5 = anova(model_all_features_all, model_reduced_no_duration)$`Pr(>Chisq)`[2]
p6 = anova(model_all_features_all, model_reduced_no_mean_intensity)$`Pr(>Chisq)`[2]
p7 = anova(model_all_features_all, model_reduced_no_sd_intensity)$`Pr(>Chisq)`[2]

p.adjust(c(p1, p2, p3, p4, p5, p6, p7), method="holm")
```


## Conventionals

```{r}

model_all_features = glmer(data = filter(df_audio, form == "conventional"),
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  slope_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())

model_reduced_no_slope = glmer(data = filter(df_audio, form == "conventional"),
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())


model_reduced_no_mean_f0 = glmer(data = filter(df_audio, form == "conventional"),
                label ~ slope_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())


model_reduced_no_range = glmer(data = filter(df_audio, form == "conventional"),
                label ~ mean_f0_z_score + 
                  slope_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())


model_reduced_no_sd_f0 = glmer(data = filter(df_audio, form == "conventional"),
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  slope_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())

model_reduced_no_duration = glmer(data = filter(df_audio, form == "conventional"),
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  slope_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())

model_reduced_no_mean_intensity = glmer(data = filter(df_audio, form == "conventional"),
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  slope_f0_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())

model_reduced_no_sd_intensity = glmer(data = filter(df_audio, form == "conventional"),
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  slope_f0_z_score +
                  (1 | topic),
                 family = binomial())

```

### Correct

```{r}
summary(model_all_features)

anova(model_all_features, model_reduced_no_slope)
anova(model_all_features, model_reduced_no_mean_f0)
anova(model_all_features, model_reduced_no_range)
anova(model_all_features, model_reduced_no_sd_f0)
anova(model_all_features, model_reduced_no_duration)
anova(model_all_features, model_reduced_no_mean_intensity)
anova(model_all_features, model_reduced_no_sd_intensity)

p1 = anova(model_all_features, model_reduced_no_slope)$`Pr(>Chisq)`[2]
p2 = anova(model_all_features, model_reduced_no_mean_f0)$`Pr(>Chisq)`[2]
p3 = anova(model_all_features, model_reduced_no_range)$`Pr(>Chisq)`[2]
p4 = anova(model_all_features, model_reduced_no_sd_f0)$`Pr(>Chisq)`[2]
p5 = anova(model_all_features, model_reduced_no_duration)$`Pr(>Chisq)`[2]
p6 = anova(model_all_features, model_reduced_no_mean_intensity)$`Pr(>Chisq)`[2]
p7 = anova(model_all_features, model_reduced_no_sd_intensity)$`Pr(>Chisq)`[2]

p.adjust(c(p1, p2, p3, p4, p5, p6, p7), method="holm")
```


## Non-conventional

```{r}

model_all_features_non = glmer(data = filter(df_audio, form == "nonconventional"),
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  slope_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())

model_reduced_no_slope_non = glmer(data = filter(df_audio, form == "nonconventional"),
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())


model_reduced_no_mean_f0_non = glmer(data = filter(df_audio, form == "nonconventional"),
                label ~ slope_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())


model_reduced_no_range_non = glmer(data = filter(df_audio, form == "nonconventional"),
                label ~ mean_f0_z_score + 
                  slope_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())


model_reduced_no_sd_f0_non = glmer(data = filter(df_audio, form == "nonconventional"),
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  slope_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())

model_reduced_no_duration_non = glmer(data = filter(df_audio, form == "nonconventional"),
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  slope_f0_z_score + 
                  mean_intensity_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())

model_reduced_no_mean_intensity_non = glmer(data = filter(df_audio, form == "nonconventional"),
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  slope_f0_z_score + 
                  sd_intensity_z_score +
                  (1 | topic),
                 family = binomial())

model_reduced_no_sd_intensity_non = glmer(data = filter(df_audio, form == "nonconventional"),
                label ~ mean_f0_z_score + 
                  range_f0_z_score + 
                  sd_f0_z_score + 
                  duration_f0_z_score + 
                  mean_intensity_z_score + 
                  slope_f0_z_score +
                  (1 | topic),
                 family = binomial())
```


## Correct for multiple comparisons

```{r}
summary(model_all_features_non)

p1 = anova(model_all_features_non, model_reduced_no_slope_non)$`Pr(>Chisq)`[2]
p2 = anova(model_all_features_non, model_reduced_no_mean_f0_non)$`Pr(>Chisq)`[2]
p3 = anova(model_all_features_non, model_reduced_no_range_non)$`Pr(>Chisq)`[2]
p4 = anova(model_all_features_non, model_reduced_no_sd_f0_non)$`Pr(>Chisq)`[2]
p5 = anova(model_all_features_non, model_reduced_no_duration_non)$`Pr(>Chisq)`[2]
p6 = anova(model_all_features_non, model_reduced_no_mean_intensity_non)$`Pr(>Chisq)`[2]
p7 = anova(model_all_features_non, model_reduced_no_sd_intensity_non)$`Pr(>Chisq)`[2]

p.adjust(c(p1, p2, p3, p4, p5, p6, p7), method="holm")
```

### Visualize

```{r}
df_audio %>%
  filter(form == "nonconventional") %>%
  ggplot(aes(x = label,
             y = duration_f0_z_score)) +
  geom_boxplot() +
  labs(x = "Speaker intent",
       y = "#Voiced Frames (Z-scored)",
       title = "#Voiced frames (non-conventional)") +
  theme_minimal()

```


# Train classifier(s)

We already know/believe that the acoustic features are predictive of people's responses, and of accuracy. We also know they interact with **form**.

Now, we test the ability of a classifier (logistic regression) to learn which features best predict **intent**. We validate its accuracy using leave-one-out cross validation (LOOCV); that is, for each item *Y*, we train the classifier on every *other* item, then try to predict *Y*. We then average the accuracy across all predicted items.


## Logistic regression

### Use Leave-one-out cross-validation

#### Baseline

```{r}
df_audio$index = c(1: nrow(df_audio))
prob_outputs = c()
for (iterating_index in c(1:nrow(df_audio))) {
  
  train = df_audio %>%
    filter(index != iterating_index)
  
  test = df_audio %>%
    filter(index == iterating_index)
  
  model_core = glm(data = train,
                  label ~ 0,
                   family = binomial())
  
  probabilities = predict(model_core, test, type="response")

  prob_outputs[iterating_index] = probabilities
}

df_audio$lr_probs = prob_outputs

df_audio$lr_prediction = ifelse(df_audio$lr_probs > 0.5,
                             "literal","request")

df_audio$lr_correct = df_audio$lr_prediction == df_audio$label
mean(df_audio$lr_correct)
```


#### All features

```{r}
df_audio$index = c(1: nrow(df_audio))
prob_outputs = c()
for (iterating_index in c(1:nrow(df_audio))) {
  
  train = df_audio %>%
    filter(index != iterating_index)
  
  test = df_audio %>%
    filter(index == iterating_index)
  
  model_core = glm(data = train,
                  label ~ mean_f0_z_score*form + range_f0_z_score*form + 
                    sd_f0_z_score*form + duration_f0_z_score*form + 
                    slope_f0_z_score*form + mean_intensity_z_score*form + 
                    sd_intensity_z_score*form,
                   family = binomial())
  
  probabilities = predict(model_core, test, type="response")

  prob_outputs[iterating_index] = probabilities
}

df_audio$lr_probs = prob_outputs

df_audio$lr_prediction = ifelse(df_audio$lr_probs > 0.5,
                             "literal","request")

df_audio$lr_correct = df_audio$lr_prediction == df_audio$label
mean(df_audio$lr_correct)
```



# Compare acoustic features to human behavior

## Extract difference scores

First we extract all differences from the z-scored features.

```{r}

df_audio$label = fct_recode(df_audio$label,
                            "Request" = "request",
                            "Non-request" = "literal")

df_audio$item = paste(df_audio$speaker, df_audio$stimNum, sep="_")

critical_audio = df_audio 
slope_IR = filter(critical_audio, label == "Request")$slope_f0_z_score
slope_literal = filter(critical_audio, label == "Non-request")$slope_f0_z_score
slope_diff = slope_IR - slope_literal

duration_f0_IR = filter(critical_audio, label == "Request")$duration_f0_z_score
duration_f0_literal = filter(critical_audio, label == "Non-request")$duration_f0_z_score
duration_f0_diff = duration_f0_IR - duration_f0_literal

sd_intensity_IR = filter(critical_audio, label == "Request")$sd_intensity_z_score
sd_intensity_literal = filter(critical_audio, label == "Non-request")$sd_intensity_z_score
sd_intensity_diff = sd_intensity_IR - sd_intensity_literal

mean_intensity_IR = filter(critical_audio, label == "Request")$mean_intensity_z_score
mean_intensity_literal = filter(critical_audio, label == "Non-request")$mean_intensity_z_score
mean_intensity_diff = mean_intensity_IR - mean_intensity_literal

mean_f0_IR = filter(critical_audio, label == "Request")$mean_f0_z_score
mean_f0_literal = filter(critical_audio, label == "Non-request")$mean_f0_z_score
mean_f0_diff = mean_f0_IR - mean_f0_literal

sd_f0_IR = filter(critical_audio, label == "Request")$sd_f0_z_score
sd_f0_literal = filter(critical_audio, label == "Non-request")$sd_f0_z_score
sd_f0_diff = sd_f0_IR - sd_f0_literal

range_f0_IR = filter(critical_audio, label == "Request")$range_f0_z_score
range_f0_literal = filter(critical_audio, label == "Non-request")$range_f0_z_score
range_f0_diff = range_f0_IR - range_f0_literal


item = filter(critical_audio, label == "Request")$item

new_df = data.frame(item, 
                    slope_diff, 
                    duration_f0_diff,
                    sd_intensity_diff,
                    mean_intensity_diff,
                    mean_f0_diff,
                    sd_f0_diff,
                    range_f0_diff)

new_df$item = factor(new_df$item)
new_df

```

## Merge datasets

```{r}

merged = merge(experimental_data, new_df, by="item")
head(merged)
merged$Correct = fct_recode(factor(merged$correct),
                            "Yes" = "1",
                            "No" = "0")

```

### Do larger differences in each feature predict higher accuracy?

```{r}
model_accuracy_full = glmer(data = merged,
                      Correct ~ slope_diff * form +
                        mean_f0_diff * form +
                       duration_f0_diff * form +
                       range_f0_diff * form +
                       sd_f0_diff * form +
                       mean_intensity_diff * form +
                       sd_intensity_diff * form +
                        form * speaker + 
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

summary(model_accuracy_full)

```

#### F0 slope

```{r}
model_accuracy_no_slope_interaction = glmer(data = merged,
                      Correct ~ slope_diff +
                        mean_f0_diff * form +
                       duration_f0_diff * form +
                       range_f0_diff * form +
                       sd_f0_diff * form +
                       mean_intensity_diff * form +
                       sd_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_accuracy_no_slope = glmer(data = merged,
                      Correct ~ mean_f0_diff * form +
                       duration_f0_diff * form +
                       range_f0_diff * form +
                       sd_f0_diff * form +
                       mean_intensity_diff * form +
                       sd_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_accuracy_full, model_accuracy_no_slope_interaction)
anova(model_accuracy_no_slope_interaction, model_accuracy_no_slope)

```

#### Mean F0

```{r}
model_accuracy_no_mean_f0_interaction = glmer(data = merged,
                      Correct ~ slope_diff * form +
                        mean_f0_diff +
                       duration_f0_diff * form +
                       range_f0_diff * form +
                       sd_f0_diff * form +
                       mean_intensity_diff * form +
                       sd_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_accuracy_no_mean_f0 = glmer(data = merged,
                      Correct ~ slope_diff * form +
                       duration_f0_diff * form +
                       range_f0_diff * form +
                       sd_f0_diff * form +
                       mean_intensity_diff * form +
                       sd_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_accuracy_full, model_accuracy_no_mean_f0_interaction)
anova(model_accuracy_no_mean_f0_interaction, model_accuracy_no_mean_f0)

```

#### F0 duration (number of voiced frames)

```{r}
model_accuracy_no_f0_dur_interaction = glmer(data = merged,
                      Correct ~ slope_diff * form +
                        mean_f0_diff * form +
                       duration_f0_diff +
                       range_f0_diff * form +
                       sd_f0_diff * form +
                       mean_intensity_diff * form +
                       sd_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_accuracy_no_f0_dur = glmer(data = merged,
                      Correct ~ slope_diff * form +
                        mean_f0_diff * form +
                       range_f0_diff * form +
                       sd_f0_diff * form +
                       mean_intensity_diff * form +
                       sd_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_accuracy_full, model_accuracy_no_f0_dur_interaction)
anova(model_accuracy_no_f0_dur_interaction, model_accuracy_no_f0_dur)

```



#### F0 range

```{r}
model_accuracy_no_f0_range_interaction = glmer(data = merged,
                      Correct ~ slope_diff * form +
                        mean_f0_diff * form +
                       duration_f0_diff * form +
                       range_f0_diff +
                       sd_f0_diff * form +
                       mean_intensity_diff * form +
                       sd_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_accuracy_no_f0_range = glmer(data = merged,
                      Correct ~ slope_diff * form +
                        mean_f0_diff * form +
                       duration_f0_diff * form +
                       sd_f0_diff * form +
                       mean_intensity_diff * form +
                       sd_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_accuracy_full, model_accuracy_no_f0_range_interaction)
anova(model_accuracy_no_f0_range_interaction, model_accuracy_no_f0_range)

```


#### SD F0

```{r}
model_accuracy_no_f0_sd_interaction = glmer(data = merged,
                      Correct ~ slope_diff * form +
                        mean_f0_diff * form +
                       duration_f0_diff * form +
                       range_f0_diff * form+
                       sd_f0_diff +
                       mean_intensity_diff * form +
                       sd_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_accuracy_no_f0_sd = glmer(data = merged,
                      Correct ~ slope_diff * form +
                        mean_f0_diff * form +
                        range_f0_diff * form+
                       duration_f0_diff * form +
                       mean_intensity_diff * form +
                       sd_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_accuracy_full, model_accuracy_no_f0_sd_interaction)
anova(model_accuracy_no_f0_sd_interaction, model_accuracy_no_f0_sd)

```

#### Mean Intensity

```{r}
model_accuracy_no_mean_intensity_interaction = glmer(data = merged,
                      Correct ~ slope_diff * form +
                        mean_f0_diff * form +
                       duration_f0_diff * form +
                       range_f0_diff * form+
                       sd_f0_diff * form +
                       mean_intensity_diff +
                       sd_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_accuracy_no_mean_intensity = glmer(data = merged,
                      Correct ~ slope_diff * form +
                        mean_f0_diff * form +
                        range_f0_diff * form+
                        sd_f0_diff * form +
                       duration_f0_diff * form +
                       sd_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_accuracy_full, model_accuracy_no_mean_intensity_interaction)
anova(model_accuracy_no_mean_intensity_interaction, model_accuracy_no_mean_intensity)

```

#### SD Intensity

```{r}
model_accuracy_no_sd_intensity_interaction = glmer(data = merged,
                      Correct ~ slope_diff * form +
                        mean_f0_diff * form +
                       duration_f0_diff * form +
                       range_f0_diff * form+
                       sd_f0_diff * form +
                       mean_intensity_diff * form +
                       sd_intensity_diff +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_accuracy_no_sd_intensity = glmer(data = merged,
                      Correct ~ slope_diff * form +
                        mean_f0_diff * form +
                        range_f0_diff * form+
                        sd_f0_diff * form +
                       duration_f0_diff * form +
                       mean_intensity_diff * form +
                        form * speaker +
                        (1 | subject) + (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_accuracy_full, model_accuracy_no_sd_intensity_interaction)
anova(model_accuracy_no_sd_intensity_interaction, model_accuracy_no_sd_intensity)
```

#### Visualizations

```{r}
merged %>%
  ggplot(aes(x = form,
             y = slope_diff,
             fill = Correct)) +
  geom_boxplot() +
  theme_minimal()

merged %>%
  ggplot(aes(x = form,
             y = mean_f0_diff,
             fill = Correct)) +
  geom_boxplot() +
  theme_minimal()
```


### Multiple comparisons correction

```{r}
p1 = anova(model_accuracy_full, model_accuracy_no_slope_interaction)$`Pr(>Chisq)`[2]
p2 = anova(model_accuracy_no_slope_interaction, model_accuracy_no_slope)$`Pr(>Chisq)`[2]
p3 = anova(model_accuracy_full, model_accuracy_no_mean_f0_interaction)$`Pr(>Chisq)`[2]
p4 = anova(model_accuracy_no_mean_f0_interaction, model_accuracy_no_mean_f0)$`Pr(>Chisq)`[2]
p5 = anova(model_accuracy_full, model_accuracy_no_f0_dur_interaction)$`Pr(>Chisq)`[2]
p6 = anova(model_accuracy_no_f0_dur_interaction, model_accuracy_no_f0_dur)$`Pr(>Chisq)`[2]
p7 = anova(model_accuracy_full, model_accuracy_no_f0_range_interaction)$`Pr(>Chisq)`[2]
p8 = anova(model_accuracy_no_f0_range_interaction, model_accuracy_no_f0_range)$`Pr(>Chisq)`[2]
p9 = anova(model_accuracy_full, model_accuracy_no_f0_sd_interaction)$`Pr(>Chisq)`[2]
p10 = anova(model_accuracy_no_f0_sd_interaction, model_accuracy_no_f0_sd)$`Pr(>Chisq)`[2]
p11 = anova(model_accuracy_full, model_accuracy_no_mean_intensity_interaction)$`Pr(>Chisq)`[2]
p12 = anova(model_accuracy_no_mean_intensity_interaction, model_accuracy_no_mean_intensity)$`Pr(>Chisq)`[2]
p13 = anova(model_accuracy_full, model_accuracy_no_sd_intensity_interaction)$`Pr(>Chisq)`[2]
p14 = anova(model_accuracy_no_sd_intensity_interaction, model_accuracy_no_sd_intensity)$`Pr(>Chisq)`[2]

p.adjust(c(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, p13, p14), method="holm")

```

